### 2023-01-18 paper-reviews/papers-2023.tex
Count total number of citations
Add an article about test case reduction in C

@@

    \cite{Pharr:ispc:2012}.
\end{itemize}

>>>>

A total of \total{citenum} papers read in the year.

@@

    \cite{Pharr:ispc:2012}.

    \item As practice shows creating a concise reproducer for a bug is sometimes as complex as fixing a bug. Compiler bugs can be especially hard to report as they are usually observed on real and rather big projects. Even relatively small \href{https://yulyugin.github.io/blog/2022/icc-bug}{compiler bug} reproducers could be hard to analyze and report. Authors of the paper tried to address this important issue by implementing an automatic test case reducers for C:

    \cite{Regehr:C-Reduce:2012}
\end{itemize}
